---
title: "mbenchmark: benchmarking the common matrix operations"
output: github_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

## Introduction

This is a generic framework for benchmarking the common matrix operations among different matrix file formats.

* subsetting
    * `region_selection`: continuous block selection
    * `random_slicing`: non-continuous slab selection
* traversing
    * `rowSums`
    * `colSums`

## Takes a list of different `matrix` containers/objects as input
The only requirements for the `matrix` object are:

* support `[` indexing method for subsetting
* `dim` accessors to retrieve dimension information

```{r message=FALSE,warning=FALSE,results='hide'}
library(mbenchmark)
mat <- matrix(seq_len(2e6), nrow = 1e3, ncol =2e3)
dims <- dim(mat)

#bigmemory
library(bigmemory)
bm.file <- tempfile()
suppressMessages(bm <- as.big.matrix(mat, backingfile = basename(bm.file), backingpath = dirname(bm.file)))
bm <- DelayedArray(bm)

#h5
library(rhdf5)
h5.file <- tempfile()
h5createFile(h5.file)
h5createDataset(h5.file, "data", dims, storage.mode = "double", chunk=c(100,100), level=7)
h5write(mat, h5.file,"data")
library(HDF5Array)
hm = HDF5Array(h5.file, "data")

library(ff)
ff.file <- tempfile()
fm <- ff(mat, vmode="double", dim=dims, filename = ff.file)

```
## Compare disk usage
```{r}
mat.list <- list(bigmemory = bm, ff = fm, h5 = hm)

utils:::format.object_size(file.size(bm.file), units = "Mb")
utils:::format.object_size(file.size(h5.file), units = "Mb")
utils:::format.object_size(file.size(ff.file), units = "Mb")

```
## Compare memory usage
```{r}
library(pryr)
lapply(mat.list, object_size)
```



## Run `subsetting` benchmark
```{r}
#ubound specify the upper bound of the size of the subset. It is the value of the maximum percentage of original matrix
res <- mbenchmark(mat.list, type = "subsetting", times = 3, ubound = 0.9, verbose = FALSE) 
```


Results are collected as a `data.table`, which is easy to query or facetting.
```{r}
head(res)
```

## Quick plot

```{r cars}
autoplot(res)
```

## Run `traversing` benchmark
```{r eval=FALSE}
mat.list <- list(bigmemory = bm, ff = fm, h5 = hm)
res <- mbenchmark(mat.list, type = "traversing")
```

## Todo
* `clear_page_cache`
* `parallel` IO
* More matrix operations